The Evolution of Phenotypically Invariant Genetic Networks

### 2017-08-29 kalman_walk_paper.tex
edited system description, qgen, examples, speciation and more.

Gene regulatory networks with identical phenotypes do not necessarily have identical kryptotypes.
Any linear and minimal gene network 
-- minimal, informally meaning that the system's phenotype is achieved with the fewest possible genes $(n=m)$
-- has an identical impulse response and thus phenotype given identical inputs $u(t)$, up to a change of coordinates. 
\plr{"has an identical phenotype" is not what you mean to say here}
\js{edited -- does that work?}
  \begin{equation}
    \begin{aligned}
      h(t) &= C e^{A t} B 
      = C V^{-1} V e^{A t} V^{-1} V B \\
      &= C V^{-1} e^{V A V^{-1} t} V B 
      = \bar{C} e^{\bar{A} t} \bar{B}
    \end{aligned}
  \end{equation}
\plr{what are we calling these -- not "biological system" -- that's too broad}\js{I see your point, but I don't want to bog down the paper by constantly qualifying statements -- it seemsnatural to refer to biological systems, since these are, afterall dynamical systems.}
Two biological systems, $\mathcal{S} = \{ A, B, C \}$, and $\bar{\mathcal{S}} = \{\bar{A} = VAV^{-1}, \bar{B} = VB, \bar{C} = CV^{-1} \}$, 
have the same phenotype, for all possible inputs, if they are related by a change of coordinates. 
\plr{is this the place to say "and only if, in the minimal dimension"?}

>>>>

Gene regulatory networks with identical phenotypes do not necessarily have identical kryptotypes.
Any linear and minimal gene network 
-- minimal, informally meaning that the system's phenotype is achieved with the fewest possible genes $(n=m)$
-- has an identical impulse response and thus phenotype given identical inputs $u(t)$, up to a change of coordinates. 
\plr{"has an identical phenotype" is not what you mean to say here}
\js{edited -- does that work?}
  \begin{equation}
    \begin{aligned}
      h(t) &= C e^{A t} B 
      = C V^{-1} V e^{A t} V^{-1} V B \\
      &= C V^{-1} e^{V A V^{-1} t} V B 
      = \bar{C} e^{\bar{A} t} \bar{B}
    \end{aligned}
  \end{equation}
Two gene networks, $\mathcal{S} = \{ A, B, C \}$, and $\bar{\mathcal{S}} = \{\bar{A} = VAV^{-1}, \bar{B} = VB, \bar{C} = CV^{-1} \}$, 
have the same phenotype, for all possible inputs, if they are related by a change of coordinates. 
\plr{is this the place to say "and only if, in the minimal dimension"?}
